**Sequencing 16S rRNA gene fragments using the PacBio SMRT DNA sequencing system**

### 2016-02-18 Schloss_PacBio16S_PeerJ_2016.Rmd
Create TeX intermediate files

---
title: "**Sequencing 16S rRNA gene fragments using the PacBio SMRT DNA sequencing system**"
bibliography: references.bib
output:
  pdf_document:
    includes:
      in_header: header.tex
csl: peerj.csl
fontsize: 11pt
geometry: margin=1.0in
---

@@

## Funding statement
This study was supported by grants from the NIH (R01HG005975, R01GM099514 and P30DK034933 to PDS and U54HG004973 to SKH).

>>>>

---
title: "**Sequencing 16S rRNA gene fragments using the PacBio SMRT DNA sequencing system**"
bibliography: references.bib
output:
  pdf_document:
    keep_tex: true
    includes:
      in_header: header.tex
csl: peerj.csl
fontsize: 11pt
geometry: margin=1.0in
---

@@
